---
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(error = FALSE)
```

```{r data}
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(knitr))
suppressPackageStartupMessages(library(BatchGetSymbols))

invisible(capture.output(daily_returns <- BatchGetSymbols(tickers = "TSLA",
  first.date = as.Date("2017-07-25"),
  last.date = Sys.Date())))

investment <- data.frame(daily_returns$df.tickers)

tsla_summ <- investment %>% 
  select(
    Ticker = ticker, 
    Date = ref.date,
    Open = price.open,
    High = price.high,
    Low = price.low,
    #Volume = volume,
    Close = price.close) %>% 
  #mutate(Value = Close - Open) %>% 
  mutate(Pct_Change = round(((Close-Open)/Open)*100, 2)) #%>% 
  #mutate(Dollar_Change = 10000*(Pct_Change/100)) %>% 
  #mutate(Profit_Total = cumsum(10000*(Pct_Change/100)))
```

<center> <h1> Pat and Aaron's $10K TSLA Experiment </h1> </center>
<br>
<br>

## Background.

Pat and Aaron like investing, but it is risky. Instead of actually investing our own hard-earned money, we decide to invest some play money. Based on the recommendation of our firm's research analyst, Lisa Baggett, M.D., Pat and Aaron decide to invest $10,000 in Tesla ([TSLA](https://finance.yahoo.com/quote/TSLA?p=TSLA)) on July 25, 2017 at a market closing price of $`r round(tsla_summ$Close[1], 2)`. <!--By comparison-->

```{r, performance}
#daily <- round(tsla_summ$Profit_Total[length(tsla_summ$Profit_Total)], 2) - 7
sell <- round(29.44641*investment$price.close[length(investment$price.close)] - 10000, 2) - 7

#updown <- ifelse(daily < 0, "down", "up")
losegain <- ifelse(sell < 0, "lose", "net")
lossgain <- ifelse(sell < 0, "loss", "gain")
```

## Performance

Including a $7.00 cost of trade, if we sold our shares today, we would **`r losegain`** $`r sell`, a `r lossgain` of `r (sell/10000)*100`%. <!--Compared to the Vanguard Total Stock Market Index (Admiral Shares), if we sold -->

```{r chart, fig.align = "center", fig.width = 10}
# Track investment performance
ggplot(daily_returns$df.tickers, aes(x = ref.date, y = price.close, color = "1")) + 
  geom_line(size = 0.75) + scale_color_manual(values = "tomato") +
  facet_wrap(~ticker, scales = 'free_y') + theme_light() +
  theme(strip.text.x = element_text(size = 17, face = "bold"),
    legend.position = "none", axis.text.x = element_text(size = 11),
    axis.text.y = element_text(size = 11),
    axis.title.y = element_text(size = 12, face = "bold")) +
  scale_x_date(name = "", date_breaks = "1 week", date_labels = "%d %b") +
  scale_y_continuous(name = "Closing Price\n")
```

<br>

```{r table}
names(tsla_summ) <- c("Ticker", "Date", "Open", "High", "Low", "Close", 
  "Daily % Change") #"Daily $ Change", "Cumulative Profit Total")
kable(tsla_summ)
```


